Model LF

### 2022-10-06 max_dp endogen stød.Rmd
commit

plot(((wage_ds_05 - wage_ds_00) / wage_ds_00), col= "black", xlab= "Year", ylab= "% Change in wage", main= "Wage");
grid()

plot((wage_gap1_05), col= "black", xlab= "Year", ylab= "% Change in compensation rate", main= "compensation rate");
grid()
```

@@

plot(((net_balance_05 - net_balance_00) / net_balance_00), col= "black", xlab= "Year", ylab= "% Change in net balance", main= "Net balance");
grid()

@@

## Scenario 3 reg part

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_part_model = TIMESERIES(shock_part_model_shock+1 ,START=c(2016,1),  FREQ='Q')

@@

yk_ds_06 = Shock_6$simulation$yk_ds
emp_06 = Shock_6$simulation$emp
wage_ds_06 = Shock_6$simulation$wage_ds
ur_ds_06 = Shock_6$simulation$ur_ds
pc_ds_06 = Shock_6$simulation$pc_ds
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
pconk_ds_06 = Shock_6$simulation$pconk_ds
komp_r_06 = Shock_6$simulation$komp_r
max_dp_06 = Shock_6$simulation$max_dp
nben_h_06 = Shock_6$simulation$nben_h
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
ik_06 = Shock_6$simulation$ik
wage_ds_t_06 = Shock_6$simulation$wage_ds_t
nben_h_un_06 = Shock_6$simulation$nben_h_un
nl_g_06 = Shock_6$simulation$nl_g
nsben_h_06 = Shock_6$simulation$nsben_h
dp_person_06 = Shock_6$simulation$dp_person
part1_06 = Shock_6$simulation$part1
u_ds_06 = Shock_6$simulation$u_ds
kont_h_ratio_06 = Shock_6$simulation$kont_h_ratio
```

@@

plot(yk_ds_06, col= "red"); lines(yk_ds_05, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

>>>>

plot(((wage_ds_t_05 - wage_ds_t_00) / wage_ds_t_00), col= "black", xlab= "Year", ylab= "% Change in Target wage", main= "Target Wage");
grid()

plot((wage_gap_05), col= "black", xlab= "Year", ylab= "Wage gap as % of target wage", main= "Wage gap");
grid()
```
```{r}
par(mfrow=c(1,2))

plot(((wage_ds_05 - wage_ds_00) / wage_ds_00), col= "black", xlab= "Year", ylab= "% Change in net balance", main= "Net balance");
grid()

@@

@@

## Scenario 3 reg kuld

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2016,1),  FREQ='Q')

@@

yk_ds_06 = Shock_6$simulation$yk_ds
emp_06 = Shock_6$simulation$emp
wage_ds_06 = Shock_6$simulation$wage_ds
ur_ds_06 = Shock_6$simulation$ur_ds
pc_ds_06 = Shock_6$simulation$pc_ds
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
pconk_ds_06 = Shock_6$simulation$pconk_ds
komp_r_06 = Shock_6$simulation$komp_r
max_dp_06 = Shock_6$simulation$max_dp
nben_h_06 = Shock_6$simulation$nben_h
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
ik_06 = Shock_6$simulation$ik
wage_ds_t_06 = Shock_6$simulation$wage_ds_t
nben_h_un_06 = Shock_6$simulation$nben_h_un
nl_g_06 = Shock_6$simulation$nl_g
nsben_h_06 = Shock_6$simulation$nsben_h
dp_person_06 = Shock_6$simulation$dp_person
part1_06 = Shock_6$simulation$part1
u_ds_06 = Shock_6$simulation$u_ds
kont_h_ratio_06 = Shock_6$simulation$kont_h_ratio
part_06 = Shock_6$simulation$part

rw_ds_06 = Shock_6$simulation$rw_ds
kuld_06 = Shock_6$simulation$shock_kuld
```

@@

plot(yk_ds_06, col= "red"); lines(yk_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

plot(((kuld_06 - kuld) / kuld), col= "black", xlab= "Year", ylab= "% Change in the insurance rate", main= "Insurance rate");
grid()

plot(((nben_h_06 - nben_h_05) / nben_h_05), col= "black", xlab= "Year", ylab= "% changes in net benefits HH", main= "Net benefits HH", sub= "Compared with scenario 1");
grid()
```

plot(((yk_ds_06 - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp");
lines()
grid()

plot(((ur_ds_06 - ur_ds_00) / ur_ds_00), col= "black", xlab= "Year", ylab= "Wage gap as % of target wage", main= "Wage gap");
grid()
```

plot(((wage_ds_t_05 - wage_ds_t_00) / wage_ds_t_00), col= "black", xlab= "Year", ylab= "% Change in Target wage", main= "Target Wage");
grid()

plot((wage_gap_05), col= "black", xlab= "Year", ylab= "Wage gap as % of target wage", main= "Wage gap");
grid()
```

plot(((wage_ds_t_05 - wage_ds_t_00) / wage_ds_t_00), col= "black", xlab= "Year", ylab= "% Change in Target wage", main= "Target Wage");
grid()

plot((wage_gap_05), col= "black", xlab= "Year", ylab= "Wage gap as % of target wage", main= "Wage gap");
grid()
```
